\documentclass[a4paper,10pt]{article}
%-----------------------------------------------------------
\usepackage[top=0.75in, bottom=0.75in, left=0.55in, right=0.85in]{geometry}
\usepackage{graphicx}
\usepackage{url}
\usepackage{palatino}
\usepackage{tabularx}
\fontfamily{SansSerif}
\usepackage{helvet}
\renewcommand{\familydefault}{\sfdefault}
\selectfont

\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}

\usepackage{enumitem}
\usepackage[geometry]{ifsym}

\usepackage{color}
\definecolor{mygrey}{gray}{0.75}
\textheight=9.75in
\raggedbottom{}

\setlength{\tabcolsep}{0in}
\newcommand{\isep}{-2 pt}
\newcommand{\lsep}{-0.5cm}
\newcommand{\sep}{-0.6cm}
\renewcommand{\labelitemii}{$\circ$}

\righthyphenmin=62
\lefthyphenmin=62
\pagestyle{empty}

\usepackage[hidelinks]{hyperref}
\urlstyle{sf}

%-----------------------------------------------------------
%Custom commands
\newcommand{\resitem}[1]{\item #1 \vspace{-2pt}}
\newcommand{\resheading}[1]{{\small \colorbox{mygrey}{\begin{minipage}{0.975\textwidth}{\textbf{#1 \vphantom{p\^{E}}}}\end{minipage}}}}
\newcommand{\ressubheading}[3]{\begin{tabular*}{6.62in}{l @{\extracolsep{\fill}} r} \textsc{{\textbf{#1}}} & \textsc{\textit{[#2]}} \\ \end{tabular*}\vspace{-8pt}}
%-----------------------------------------------------------
\begin{document}
\hspace{0.5cm}\\[-0.2cm]


% \hfill{\href{mailto:harveyormston@me.com}{harveyormston@me.com}}}}\\[\lsep]
% \resheading{\textbf{Harvey Ormston \hfill{harveyormston@me.com}}}\\[\lsep]
\resheading{\textbf{Harvey Ormston \hfill{\href{mailto:harveyormston@me.com}{\nolinkurl{harveyormston@me.com}}}}}\\[\lsep]
\\
\begin{itemize}[align=left]
\item[]Creative and enthusiastic career level Hardware/Software Engineer and
  Manager with a strong appreciation of development and manufacturing
    integration life-cycles. Excellent systems and test engineering knowledge as
    well as proven leadership qualities. An innovator, who works well in a team
    environment but also a decision maker who can act autonomously. Accustomed
    to a very deadline driven environment, dealing face to face with customers
    at a technical level and regular travel as required by business needs.
\\
\end{itemize}

\resheading{\textbf{Key Skills}}\\[\lsep]
\\
\begin{itemize}[label=\FilledSmallSquare, leftmargin=50pt]
\item Software and hardware test development
\item Programming (Python, C, C++, Matlab, bash)
\item Digital Signal Processing (DSP) and Embedded Software (ARM Cortex-M, etc)
\item Algorithm evaluation, Data Analysis and Audio Quality measurement
\item Software development tools and processes (Jira, git, svn, Jenkins, pytest, make, Vagrant)
\item Project / Team Management
\item Mobile software platforms (iOS)
\item Web stack (http, html/css, Apache/Tomcat, JMeter, Flask)
\item Wireless communications protocols (BLE, GSM, C2K, WCDMA)
\item Strong *nix CLI user/administrator
\\
\end{itemize}

\resheading{\textbf{Career History}}\\[\lsep]

\begin{itemize}[align=left]
\item[] \textbf{2011 – present: Dialog Semiconductor, Principal DSP Software Verification Engineer}
\item[] Dialog Semiconductor creates energy-efficient, highly integrated,
  mixed-signal circuits optimised for personal portable, short-range wireless,
    lighting, display and automotive applications. At Dialog, I help lead the
    test activity for DSP Software and Hardware.
\\
\end{itemize}

\begin{itemize}[label=\FilledSmallSquare, leftmargin=50pt]
\item Specify, plan and execute testing of DSP and Embedded Software.
\item Develop software (in Python, C and C++) for the purpose of test automation.
\item Perform analysis and characterisation of DSP algorithms such as Active Noise Cancellation (ANC), Dynamic Range Compression, Sensor Fusion, Asynchronous Sample Rate Conversion, EQ/Filtering and many others.
\item Provide assessment of the quality (both subjective and objective) of algorithms and explore opportunities for improvement where necessary.
\item Control Continuous Integration (using Jenkins) and Release of Software and Hardware deliverables.
\item Perform system level test and hardware-based evaluation.
\item Benchmark software against market competitor solutions and profile for performance (MIPS, memory footprint, power consumption, etc)
\item Work with lab equipment including the Audio Precision APx series to perform audio quality measurements.
\item Devise automated bench experiments using measurement hardware where required.
\\
\end{itemize}

\begin{itemize}[align=left]
\item[] \textbf{2004 – 2011: I-play / Oberon Media, QA Manager / Producer}
\item[] I-play’s primary business was the development and publishing of games
  for mobile handsets. At I-play, I was responsible for QA processes and
    project delivery across the global Reference development division, managing
    a team of up to 40 test engineers and leads in up to 6 different sites.
\\
\end{itemize}

\begin{itemize}[label=\FilledSmallSquare, leftmargin=50pt]
\item Work with Production and R\&D teams to test new technologies and product features.
\item Identify requirements and opportunities for process improvement within the QA department and provide documentation and tools to assist project teams.
\item Provide administrative and development support for all testing tools (bug database, TCM tools, build management, version control, automated test, etc).
\item Plan, project manage and deploy QA resources across, on average, 6 concurrently running projects in various stages of development.
\item Monitor test activity and provide technical or strategic judgements, assessing the impact of issues.
\item Hire and train new testing staff. Lead on-going training and improvement of existing staff.
\\
\end{itemize}

\begin{itemize}[align=left]
\item[] \textbf{2000 – 2003: Agilent Technologies, New Product Systems Engineer / Product Engineer}
\item[] I worked on the manufacturing team for Agilent’s 8960 wireless
  communications test set. This product delivers test/laboratory development
    and protocol analysis solutions for digital and analogue cellular
    modulation formats.
\\
\end{itemize}

\begin{itemize}[label=\FilledSmallSquare, leftmargin=50pt]
\item Test definition and development.
\item System characterisation to ensure suitability for integration into Final Test environment.
\item Development (definition of test methodology) and implementation (in software) of suitable qualification/production tests for RF Source hardware.
\item Exhaustive parametric characterisation of Baseband RF Source hardware by programming complex, multi-variable measurement routines and experiments.
\item Development of software tools and documentation to assist in production diagnostics.
\\
\end{itemize}

\resheading{\textbf{Education and Qualifications} }\\[\lsep]
\\
\begin{itemize}
  \item[] BEng (Hons) Electronics and Electrical Engineering, The University of Edinburgh (1996 – 2000)
\item[] Systems Engineering, Signal Processing, Systems Theory, Radio Frequency
  Engineering, Digital Communications, Circuit Theory, Microelectronic Devices,
    Electromagnetics, Product Studies, Power Electronics, Computer Science.
\\
\end{itemize}

\resheading{\textbf{Activities \& Interests} }\\[\lsep]
\\
\begin{itemize}
\item[] I enjoy programming in my spare time and am active in audio and games
  software development. I have a keen interest in music and run a small
    home-based recording studio. Other interests include reading, cinema and
    swimming. I have an intermediate knowledge of German.
\\
\end{itemize}

\end{document}
